\documentclass[12pt]{article}


\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\date{}

\newcommand{\mys}[2]{\displaystyle\sum_{#1}^{#2}}

\usepackage{tikz}

\newif\ifans
\anstrue


\begin{document}

\begin{center}
  \textbf{COMS 3110: Homework 0}\\
  \textbf{Due: September $13^{th}$, 11:59pm}\\
  \textbf{Total Points: 5}
\end{center}


\paragraph{Late submission policy.\ }
An assignment that is submitted one day late will get a penalty of $10\%$. An assignment that is submitted two days late will get a penalty of $20\%$. Assignments submitted after two days will not be graded and will get no points. For example, if an assignment is due on Friday by midnight, a submission on Saturday will be penalized by $10\%$, and a submission on Sunday will be penalized by $20\%$. A submission on Monday will get no points. 

\paragraph{Submission format.\ }
Homework solutions will have to be typed. You can use word, LaTeX, or any other type-setting tool to type your solution. Your submission file should be in pdf format. Do \textbf{NOT} submit a photocopy of handwritten homework except for diagrams that can be hand-drawn and scanned. We reserve the right \textbf{NOT} to grade homework that does not follow the formatting requirements.
Name your submission
file: \texttt{<Your-net-id>-3110-hw0.pdf}. For instance, if your netid
is \texttt{asterix}, then your submission file will be named
\texttt{asterix-3110-hw0.pdf}.
Each student must hand in their own assignment. If you discussed the homework or solutions with others, a list of collaborators must be included with each submission. Each of the collaborators has to write the solutions in their own words (copies are not allowed).\\ \\
\textbf{If you do not sign and date this homework, you get ZERO points.}

\begin{itemize}
    \item I have read the syllabus instructions on how to work on homework assignments, how to submit a homework assignment, and the late penalty policy.

    \item You are expected to do homework assignments by yourself, but you can discuss general concepts and questions with your classmates (read the syllabus).

    \item It is not the responsibility of the instructors, or the TAs, or the tutors to solve your homework problems. That is your responsibility.

    \item The above resources are available during office hours to answer questions about the lectures, to help understand concepts, and to help with recitation problems.

    \item Clarification on homework problems will be posted on Piazza. Please sign up on Piazza as soon as possible.

    \item We will give you help with recitation problems only if you produce your recitation notebook or other documentation indicating that you have made an honest attempt at working through the recitation problems.

    \item I understand all the bullet points above.
\end{itemize}

\noindent\begin{tabular}{ll}
\makebox[2.5in]{\hrulefill} & \\
Name & \\[8ex]% adds space between the two sets of signatures
\makebox[2.5in]{\hrulefill} & \makebox[2.5in]{\hrulefill}\\
Signature & Date\\
\end{tabular}
\end{document}




%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
